Cybersecurity Is Too Important\\To Be Left To The Specialists

### 2019-02-26 FIE2019.tex
Added Sections to table

This is not a brand-new concern: see \cite{Parr2014a} for concerns over five years ago, but it is a growing one. On the one hand, GDPR has increased the corporate penalties for failure, and therefore the demand for various forms of Cybersecurity specialists, both explicitly by requiring Data Protection Officers\footnote{\cite{EU292016a} places quite strong requirements on these: ``expertise in national and European data protection laws and practices and an in-depth understanding of the GDPR'', as well as ``principles of data processing'', ``data protection by design and by default'' and ``security of processing''. It is hard to envisage one person possessing all these attributes, and indeed ``DPO as a service'' is being promoted \cite{McCreanor2018d}.} and implicitly by causing boards to invest more in Cybersecurity. On the other hard, the growing publicity given to these, and the growing use of electronic payment, has also led to greater demand for staff in this area.

@@

In recent years the BCS has evolved its Accreditation Practices to promote and mandate the inclusion of Cybersecurity within the programmes the body accredits. The timeline which this process has followed in Table \ref{table:1} .
\begin{center}
  \begin{table}[h!]
  \begin{tabular}{ | p{6cm} |p{1.5cm} |}
    \hline
    Developing Expectations &   \\ \hline
    UK Government Cybersecurity Strategy \cite{UKCabinetOffice} & November 2011 \\ \hline
    Three workshops of a consortium of industry, academia and government bodies - led by CPHC and (ISC)2 - leading to the development of Cybersecurity learning guidelines to be embedded into BCS accredited UK Computer Science and IT-related degree \cite{CPHCISC2}  & 2013 to June 2015 \\ \hline
    UK Government report Cybersecurity Skills, Business Perspectives and Government's Next Steps Report Released \cite{UKCabinetOffice2014} & March 2014  \\ \hline
    Council of Professors and Heads of Computing (CPHC) Identifies Cybersecurity as one the top 3 concerns in Computing & April 2014 \\ \hline
    Joint Development of White Paper from CPHC and The International Information Systems Security Certification Consortium(ISC)2 \cite{CPHCISC2014} & April -November 2014 \\ \hline
    Extended Cybersecurity Criteria included in BCS Accreditation Guidelines \cite{BCS2018a}& June 2015 \\
    \hline
    What does the BCS tell Universities? & \\ \hline
    Cybersecurity Principles Roadshow & March-April 2016 \\ \hline
    Accreditation - what progress has been made? &  \\ \hline
    All visited HEIs expected to be fully compliant & September 2020 (BCS follow a 5-year Accreditation Cycle)  \\ \hline
  \end{tabular}
  \caption{Timeline of the development of Cybersecurity expectations}
  \label{table:1}
  \end{table}
\end{center}
\subsection{Developing Expectations}
Internationally the expectations regarding both the breadth and depth of the expected Cybersecurity coverage has been the subject of much discussion, debate and analysis. Like many Governments, the UK Goverment has been actively been seeking ways to address this \cite{UKCabinetOffice}, \cite{UKCabinetOffice2014}. In parallel to the work complete by the ACM \cite{ACM2013a}, in the UK considerable effort was taken to ensure Industry, Higher Education, Government and the related Professional Bodies collaborated on a set of guidelines which are to the benefit of the various stakeholders and wider society \cite{Irons2016}. In 2013, an initiative was set up by (ISC)2, CPHC (the representative body of Computer Science Departments) and the Cabinet Office to examine embedding Cybersecurity into undergraduate degrees in the UK. Three workshops in 2013 and 2015 attempted to define the principles of Cybersecurity education and proposed a framework for embedding these principles in UK Computing Science curricula. Attendees at the workshops included industry, professional bodies, UK government departments and more than 30 Universities that offer undergraduate Computing Science degrees. This work intially lead to a white paper related to a proposal in the form of a whitepaper \cite{CPHCISC2014}, followed by a set of guidelines \cite{CPHCISC2}. The BCS agreed to adopt the outputs into their accreditation criteria. This was the first time that Cybersecurity has been extensively referenced within accreditation criteria for computing and IT-related degrees. The fact that Cybersecurity is included as a  component of the BCS accreditation criteria, reflects the importance placed on Cybersecurity and the expectation that all computing graduates should have knowledge and skills in Cybersecurity as they move towards Chartered status.

>>>>

This is not a brand-new concern: see \cite{Parr2014a} for concerns over five years ago, but it is a growing one. On the one hand, GDPR has increased the corporate penalties for failure, and therefore the demand for various forms of Cybersecurity specialists, both explicitly by requiring Data Protection Officers\footnote{\cite{EU292016a} places quite strong requirements on these: ``expertise in national and European data protection laws and practices and an in-depth understanding of the GDPR'', as well as ``principles of data processing'', ``data protection by design and by default'' and ``security of processing''. It is hard to envisage one person possessing all these attributes, and indeed ``DPO as a service'' is being promoted \cite{McCreanor2018d}.} and implicitly by causing boards to invest more in Cybersecurity. On the other hard, the growing publicity given to these, and the growing use of electronic payment, has also led to greater demand for staff in this area.
% JHD what are these?  Also the next paragraph needs thinking about

@@

In recent years the BCS has evolved its Accreditation Practices to promote and mandate the inclusion of Cybersecurity within the programmes the body accredits. The timeline which this process has followed in Table \ref{table:1} .
\begin{center}
  \begin{table}[h!]
  \begin{tabular}{ | p{6cm} |p{1.5cm} |}
    \hline
    IV. ACCREDITATION:RQ3 - A. Developing Expectations &   \\ \hline
    UK Government Cybersecurity Strategy \cite{UKCabinetOffice} & November 2011 \\ \hline
    Three workshops of a consortium of industry, academia and government bodies - led by CPHC and (ISC)2 - leading to the development of Cybersecurity learning guidelines to be embedded into BCS accredited UK Computer Science and IT-related degree \cite{CPHCISC2}  & 2013 to June 2015 \\ \hline
    UK Government report Cybersecurity Skills, Business Perspectives and Government's Next Steps Report Released \cite{UKCabinetOffice2014} & March 2014  \\ \hline
    Council of Professors and Heads of Computing (CPHC) Identifies Cybersecurity as one the top 3 concerns in Computing & April 2014 \\ \hline
    Joint Development of White Paper from CPHC and The International Information Systems Security Certification Consortium(ISC)2 \cite{CPHCISC2014} & April -November 2014 \\ \hline
    Extended Cybersecurity Criteria included in BCS Accreditation Guidelines \cite{BCS2018a}& June 2015 \\
    \hline
    IV. ACCREDITATION:RQ3 - B. What does the BCS tell Universities? & \\ \hline
    Cybersecurity Principles Roadshow & March-April 2016 \\ \hline
    IV. ACCREDITATION:RQ3 - C. Accreditation - what progress has been made? &  \\ \hline
    All visited HEIs expected to be fully compliant & September 2020 (BCS follow a 5-year Accreditation Cycle)  \\ \hline
  \end{tabular}
  \caption{Timeline of the development of Cybersecurity expectations}
  \label{table:1}
  \end{table}
\end{center}
\subsection{Developing Expectations}
Internationally the expectations regarding both the breadth and depth of the expected Cybersecurity coverage has been the subject of much discussion, debate and analysis. Like many Governments, the UK Goverment has been actively been seeking ways to address this \cite{UKCabinetOffice}, \cite{UKCabinetOffice2014}. In parallel to the work complete by the ACM \cite{ACM2013a}, in the UK considerable effort was taken to ensure Industry, Higher Education, Government and the related Professional Bodies collaborated on a set of guidelines which are to the benefit of the various stakeholders and wider society \cite{Irons2016}. In 2013, an initiative was set up by (ISC)2, CPHC (the representative body of Computer Science Departments) and the Cabinet Office to examine embedding Cybersecurity into undergraduate degrees in the UK. Three workshops in 2013 and 2015 attempted to define the principles of Cybersecurity education and proposed a framework for embedding these principles in UK Computing Science curricula. Attendees at the workshops included industry, professional bodies, UK government departments and more than 30 Universities that offer undergraduate Computing Science degrees. This work intially lead to a white paper related to a proposal in the form of a whitepaper \cite{CPHCISC2014}, followed by a set of guidelines \cite{CPHCISC2}. The BCS agreed to adopt the outputs into their accreditation criteria. This was the first time that Cybersecurity has been extensively referenced within accreditation criteria for computing and IT-related degrees. The fact that Cybersecurity is included as a  component of the BCS accreditation criteria, reflects the importance placed on Cybersecurity and the expectation that all computing graduates should have knowledge and skills in Cybersecurity as they move towards Chartered status.
